Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-03 MS/ms.Rmd
Writing some conclusions to hopefully better capture the goals. Also, a box would be really good and then we can use the Q10 effect sizes to walk reader through. Box can be more general, and maybe use a different effect size like SMD.

---
title: "Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology"
bibliography: ../bib/refs.bib
csl: ../bib/the-journal-of-experimental-biology.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: no
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatment. The most we can say about it, is that the effect is small, moderator of large out of the sample of effect sizes extracted from this set of studies. In the next section, we show how to 'correct' the overall effect size so that its interpretation is more meaningful.

@@

Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis as explained above <!--- if you have not done so, please do --->. The $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of known heterogeneity at the effect size level <!--- note what level's variation it accounts for depends on the type of a fixed effect or moderator --->, driven by continuous moderators such as dosage, temperature, salinity, and even pH. $I^2_{hetero}$ maybe a useful measure to provide to help readers understand just how much effect variation can result from the specific treatment application. <!--- you can also say metaAider and orcharRd packages have functions to cacualte this already via metafor - implemention is important --->

## **Conclusions and Future Directions**

>>>>

---
title: "Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology"
bibliography: ../bib/refs.bib
csl: ../bib/the-journal-of-experimental-biology.csl
output: 
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: no
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

@@

Of course, the overall effect does not provide us a way to interpret its magnitude in the context of how much CORT has been applied in the treatment. The most we can say about it, is that the effect is small, moderate or large out of the sample of effect sizes extracted from this set of studies. In the next section, we show how to 'correct' the overall effect size so that its interpretation is more meaningful.

@@

Note that this formula does not include $\sigma^2_{m}$ as sampling error variance is assumed to be known in meta-analysis as explained above <!--- if you have not done so, please do --->. The $R^2_{marginal}$ provides a formal means to assess just how much variation in effects is the result of known heterogeneity at the effect size level <!--- note what level's variation it accounts for depends on the type of a fixed effect or moderator --->, driven by continuous moderators such as dosage, temperature, salinity, and even pH. $R^2_{marginal}$, or how we like to think of it, $R^2_{heterogenity}$, maybe a useful measure to provide to help readers understand just how much effect variation can result from the specific treatment application. If the heterogeneity is high as a result, say, dosages differences, then it is clear that the choice of dosage within and across studies will have a critical impact on the effect of interest. <!--- you can also say metaAider and orcharRd packages have functions to cacualte this already via metafor - implemention is important --->

## **Conclusions and Future Directions**
Comparative physiologists are intersted in meta-analysing effects across a diversity of species, experimental approaches / designs and environments. While an overall meta-analytic mean may be of interest, more often than not, understanding the drivers of effect size heterogenity will be the primary interest. However, obvious drivers of effect size heterogenity, such as temperature and dosage differences across studies, may not really be of interest. Indeed, comparative physiolgists are likely to want an effect size or analytical approach that allows them to remove these 'nusances'. Here, we provide comparative physiologists with a set of tools to deal with 'nusance heterogenity' by creatively 'reinventing' standard effect sizes or using meta-regerssion models. Of course, nusance heterogenity might in of itself be the main interest, in which case standard meta-regression approaches will work sufficiently. However, in many cases, comparative physiolgists might simply want to focus on bigger, more interesting biological moderators of effect size direction and magnitude. However, estimating complex meta-regression models with a multitude of fixed effects might result in more challenging model interpretation. As such, a combined approach, where some of the known heterogenity is dealt with by deriving a variant effect size and associated sampling variance, and other biologically interesting moderators are fit in a meta-regerssin model, might be the desired. Indeed, this may even be a necessity to simplify the model.
